Ground state energy of quantum dots using the coupled cluster method

### 2018-06-06 project_2/article/article.tex
Add results for N = 2

    \begin{table}
        \centering
        \caption{N = 2}
        \begin{ruledtabular}
            \begin{tabular}{c|c|ccc}
                $\omega$ & $R$ & RHF & CCD(HO) & CCD(HF)

            \end{tabular}
        \end{ruledtabular}
        \label{tab:N2}        
    \end{table}

>>>>

    \subsection{Ground state energies for two-dimensional quantum dots}
        Here we show the ground state energies for the two-dimensional quantum
        dots using restriced Hartree-Fock (RHF), coupled cluster doubles using
        both the harmonic oscillator basis and the Hartree-Fock basis which we
        construct after running the RHF-method. We have chosen the convergence
        criteria to be $\num{1e-6}$ in our results for the sake of comparison
        with M. P. Lohne\cite{lohne2011ab}.

    \begin{table}
        \centering
        \caption{N = 2}
        \begin{ruledtabular}
            \begin{tabular}{c|c|ccc}
                $\omega$ & $R$ & RHF & CCD(HO) & CCD(HF) \\
                \hline
                           &  $1$  & $0.596333$ & $0.596333$ & $0.596333$ \\
                           &  $2$  & $0.596333$ & $0.512520$ & $0.512520$ \\
                           &  $3$  & $0.526903$ & $0.505972$ & $0.442235$ \\
                           &  $4$  & $0.526903$ & $0.499216$ & $0.442011$ \\
                           &  $5$  & $0.525666$ & $0.497172$ & $0.443293$ \\
                           &  $6$  & $0.525666$ & $0.494232$ & $0.443145$ \\
                     $0.1$ &  $7$  & $0.525635$ & $0.493142$ & $0.443056$ \\
                           &  $8$  & $0.525635$ & $0.491895$ & $0.442981$ \\
                           &  $9$  & $0.525635$ & $0.491262$ & $0.442927$ \\
                           &  $10$ & $0.525635$ & $0.490649$ & $0.442886$ \\
                           &  $11$ & $0.525635$ & $0.490262$ & $0.442853$ \\
                           &  $12$ & $0.525635$ & $0.489918$ & $0.442827$ \\
                \hline

                           &  $1$  & $1.886227$ & $1.886227$ & $1.886227$ \\
                           &  $2$  & $1.886227$ & $1.786914$ & $1.786914$ \\
                           &  $3$  & $1.799856$ & $1.778903$ & $1.681979$ \\
                           &  $4$  & $1.799856$ & $1.760117$ & $1.673881$ \\
                           &  $5$  & $1.799748$ & $1.754385$ & $1.670053$ \\
                           &  $6$  & $1.799748$ & $1.748232$ & $1.667804$ \\
                     $0.5$ &  $7$  & $1.799745$ & $1.745231$ & $1.666474$ \\
                           &  $8$  & $1.799745$ & $1.742548$ & $1.665494$ \\
                           &  $9$  & $1.799743$ & $1.740860$ & $1.664805$ \\
                           &  $10$ & $1.799743$ & $1.739444$ & $1.664270$ \\
                           &  $11$ & $1.799742$ & $1.738416$ & $1.663856$ \\
                           &  $12$ & $1.799742$ & $1.737562$ & $1.663522$ \\
                \hline

                           &  $1$  & $3.253314$ & $3.253314$ & $3.253314$ \\
                           &  $2$  & $3.253314$ & $3.152328$ & $3.152328$ \\
                           &  $3$  & $3.162691$ & $3.141827$ & $3.039048$ \\
                           &  $4$  & $3.162691$ & $3.118679$ & $3.025273$ \\
                           &  $5$  & $3.161921$ & $3.110967$ & $3.017944$ \\
                           &  $6$  & $3.161921$ & $3.103338$ & $3.013923$ \\
                     $1.0$ &  $7$  & $3.161909$ & $3.099324$ & $3.011405$ \\
                           &  $8$  & $3.161909$ & $3.095916$ & $3.009621$ \\
                           &  $9$  & $3.161909$ & $3.093662$ & $3.008343$ \\
                           &  $10$ & $3.161909$ & $3.091818$ & $3.007357$ \\
                           &  $11$ & $3.161909$ & $3.090436$ & $3.006590$ \\
                           &  $12$ & $3.161909$ & $3.089299$ & $3.005970$ \\
                \hline

                           &  $1$  & $5.772454$ & $5.772454$ & $5.772454$ \\
                           &  $2$  & $5.772454$ & $5.671234$ & $5.671234$ \\
                           &  $3$  & $5.679048$ & $5.658272$ & $5.553528$ \\
                           &  $4$  & $5.679048$ & $5.631669$ & $5.534333$ \\
                           &  $5$  & $5.677282$ & $5.622092$ & $5.523490$ \\
                           &  $6$  & $5.677282$ & $5.613118$ & $5.517552$ \\
                     $2.0$ &  $7$  & $5.677206$ & $5.608130$ & $5.513709$ \\
                           &  $8$  & $5.677206$ & $5.604026$ & $5.511012$ \\
                           &  $9$  & $5.677204$ & $5.601216$ & $5.509050$ \\
                           &  $10$ & $5.677204$ & $5.598946$ & $5.507540$ \\
                           &  $11$ & $5.677204$ & $5.597213$ & $5.506356$ \\
                           &  $12$ & $5.677204$ & $5.595791$ & $5.505399$ \\
            \end{tabular}
        \end{ruledtabular}
        \label{tab:N2}
    \end{table}
